Concurrent Programming with Harmony

### 2020-07-27 book/paper.tex
Added more python-like operators

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{subseq($t$, $b$, $b$)} & return a \emph{slice} of list $t$ starting
at index $b$ and ending just before index $f$\\
\hline
\texttt{append($t$, $e$)} & append $e$ to list $t$\\
\hline
\texttt{head($t$)} & return the first element of list $t$\\
\hline
\texttt{tail($t$)} & return all but the first element of list $t$\\
\hline
\texttt{listQsort($t$)} & sort list $t$ using quicksort\\
\hline
\texttt{list2bag($t$)} & convert list $t$ into a bag \\
\hline
\texttt{list2set($t$)} & convert list $t$ into a set \\
\hline
\texttt{listMin($t$)} & return the minimum of all elements in $t$\\
\hline
\texttt{listMax($t$)} & return the maximum of all elements in $t$\\
\hline
\texttt{listSum($t$)} & return the sum of all elements in $t$\\
\hline
\end{tabular}

>>>>

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{subseq($t$, $b$, $b$)} & return a \emph{slice} of list $t$ starting
at index $b$ and ending just before index $f$\\
\hline
\texttt{append($t$, $e$)} & append $e$ to list $t$\\
\hline
\texttt{head($t$)} & return the first element of list $t$\\
\hline
\texttt{tail($t$)} & return all but the first element of list $t$\\
\hline
\texttt{reversed($t$)} & reverse a list \\
\hline
\texttt{sorted($t$)} & sorted set or list \\
\hline
\texttt{set($t$)} & convert values of a dict or list into a set \\
\hline
\texttt{list($t$)} & convert set into a list \\
\hline
\texttt{values($t$)} & convert values of a dict into a list sorted by key \\
\hline
\texttt{enumerate($t$)} & like Python enumerate \\
\hline
\texttt{sum($t$)} & return the sum of all elements in $t$\\
\hline
\texttt{list2bag($t$)} & convert list $t$ into a bag \\
\hline
\texttt{listQsort($t$)} & sort list $t$ using quicksort\\
\hline
\end{tabular}
